$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-01-28 paper/e6ssm-tuning-paper.tex
Fixed a typo

The impact of gauge kinetic mixing in the case where both of the extra
U(1)'s appearing from the breakdown of E$_6$ are present at low energy
was studied in \cite{Rizzo:2012rf}.  The E$_6$SSM was also included in
a studies looking at how first or second generation sfermion masses
can be used to constrain the GUT scale parameters \cite{Miller:2012vn}
and the renormalization of VEVs \cite{Sperling:2013eva,
  Sperling:2013xqa}.  The particle spectrum and collider signatures of
the cE$_6$SSM have been studied in a series of
papers,
\cite{Athron:2009ue,Athron:2009bs,Athron:2011wu,Athron:2012sq}. The
threshold corrections to the $\overline{DR}$ gauge and Yukawa
couplings in the E$_6$SSM have also been calculated and their numerical impact in
the constrained version examined \cite{Athron:2012pw}.
%%%%%%%%%%%%%%%%%%---inserted from introduction---%%%%%%%%%%%%%%%%5%%

>>>>

The impact of gauge kinetic mixing in the case where both of the extra
U(1)'s appearing from the breakdown of E$_6$ are present at low energy
was studied in \cite{Rizzo:2012rf}.  The E$_6$SSM was also included in
studies looking at how first or second generation sfermion masses
can be used to constrain the GUT scale parameters \cite{Miller:2012vn}
and the renormalization of VEVs \cite{Sperling:2013eva,
  Sperling:2013xqa}.  The particle spectrum and collider signatures of
the cE$_6$SSM have been studied in a series of
papers,
\cite{Athron:2009ue,Athron:2009bs,Athron:2011wu,Athron:2012sq}. The
threshold corrections to the $\overline{DR}$ gauge and Yukawa
couplings in the E$_6$SSM have also been calculated and their numerical impact in
the constrained version examined \cite{Athron:2012pw}.
%%%%%%%%%%%%%%%%%%---inserted from introduction---%%%%%%%%%%%%%%%%5%%
